### 2021-08-23 README.rmd
many changes and corrections for raster support and extended spatial analysis of results. Part1
Minor edits for CRAN submission !

Philippe Apparcio, Laboratoire d'Équité Environnemental INRS (CANADA), Email: philippe.apparicio@ucs.inrs.ca

@@

Provides functions to apply Spatial Fuzzy c-means 
Algorithm, visualize and interpret results. This method is 
well suited when the user wants to analyze data with a 
fuzzy clustering algorithm and to account for the spatial dimension of 
the dataset. Indexes for measuring the spatial consistency and classification 
quality are proposed in addition. The algorithms were developed first for 
brain imagery as described in the articles of [Cai and al. 2007](https://doi.org/10.1016/j.patcog.2006.07.011) and [Zaho and al. 2013](https://doi.org/10.1016/j.dsp.2012.09.016). [Gelb and Apparicio](https://doi.org/10.4000/cybergeo.36414) proposed to apply the method to perform a socio-residential and environmental taxonomy in Lyon (France).

@@

@@

#### Spatial inconsistency

>>>>

Philippe Apparicio, Laboratoire d'Équité Environnemental INRS (CANADA), Email: philippe.apparicio@ucs.inrs.ca

@@

Provides functions to apply Spatial Fuzzy c-means 
Algorithm, visualize and interpret results. This method is 
well suited when the user wants to analyze data with a 
fuzzy clustering algorithm and to account for the spatial dimension of 
the dataset. In addition, indexes for measuring the spatial consistency and classification 
quality are proposed. The algorithms were developed first for 
brain imagery as described in the articles of [Cai and al. 2007](https://doi.org/10.1016/j.patcog.2006.07.011) and [Zaho and al. 2013](https://doi.org/10.1016/j.dsp.2012.09.016). [Gelb and Apparicio](https://doi.org/10.4000/cybergeo.36414) proposed to apply the method to perform a socio-residential and environmental taxonomy in Lyon (France). The methods can be applied to dataframes or to rasters.

@@

#### Classification consistency

To assess the stability of the obtained clusters, a function for bootstrap validation is proposed: `boot_group_validation`. The results can be used to verify if the obtained clusters are stable and how much their centres vary.

@@

#### Spatial diagnostic

Several spatial indices can be calculated to have a better spatial understanding of the obtained clusters, like the global or local Moran I calculated on the membership values, or the join-count-test on the most likely group for each observation. ELSA and Fuzzy ELSA statistics can also be calculated to identify areas with high or low multidimensional spatial autocorrelation in the membership values. See functions `spConsistency`, `calcELSA`, `calcFuzzyELSA` and `spatialDiag`.
